Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean in the United States

### 2017-08-30 doc/manuscript/manuscript.Rmd
Add comment on potential pathway for spread

The results show several genotypes shared across populations, except for Mexico and two states that had fewer than three samples each (Fig. \@ref(community-graph)).
Our network-based approach by treating the genotypes as edges and weighting each edge with the inverse of $P_{sex}$ treated the edges as springs connecting the populations with the strength proportional to the probability of obtaining the same genotype as a clone. 
This allowed us to use a graph walking algorithm to see how close the populations were simply based off of the proportion of clones they shared.
The most abundant genotype was shared across four populations, but its high value of $P_{sex}$ meant that it did not contribute significantly to the overall structure. 
The graph walking algorithm was able to divide the network into three groups, but had a modularity of 0.17, which indicates that the groups are only weakly differentiated.
This indicates that multilocus genotypes are widespread across the United States, giving more evidence for a clonal population structure.

@@

These patterns may reflect the degree of innoculum exchange among white mold screening nurseries.
One possible explanation for these overlapping patterns of uncertainty could be that sclerotia from the source fields (where breeders would bulk their seed) were being transplanted to test fields.
Because records of these fields were not kept for these purposes, it was not possible to test this hypothesis.
Another explanation could be that the breeders were all obtaining innoculum from the same source.
As the purpose of the wmn was to test the resistance of new bean varieties, the breeders needed to ensure that there was enough innoculum pressure in the field to induce disease. 
To acheive this, it was not uncommon for breeders to innoculate their fields with sclerotia from anyone who had it. 
These hypotheses, however, do not explain why regional fields are not significantly differentiated and share genotypes with wmn.

@@

<!-- From the DAPC, we extracted 6 loci that had alleles contributing more than the upper 95% quantile of the principal component loadings to either of the first two discriminant axes and found that the alleles with an allele frequency of > 50% in 2007 were reduced to < 10% in 2008, replaced by an allele that was > 2 mutational steps away (Supplementary Information). -->
<!-- This could be due to several reasons which include mis-labeling of source material or introduction of migrant sclerotia in plant material. -->

Except for the WA Region, populations that were sampled across several years appeared to be relatively stable over time with overlapping distributions in the DAPC (i.e. NE and MI, Fig. \@ref(DAPC-RY)). 
DAPC is based on the principal components of Euclidean distance between genotypes [@jombart2010discriminant]. 
Unlike Bruvo's distance, Euclidean distance does not take into account the magnitude of the difference between alleles, which could inflate the distance measure in the presence of private alleles [@bruvo2004simple]. 
We found no evidence of private alleles in the Mexico and CA isolates, suggesting that this pattern separating these populations from the others was not an artifact.

>>>>

The results show several genotypes shared across populations, except for Mexico and two states that had fewer than three samples each (Fig. \@ref(community-graph)).
Our network-based approach by treating the genotypes as edges and weighting each edge with the inverse of $P_{sex}$ treated the edges as springs connecting the populations with the strength proportional to the probability of obtaining the same genotype as a clone. 
This allowed us to use a graph walking algorithm to see how close the populations were simply based off of the proportion of clones they shared.
The most abundant genotype was shared across four populations, but its high value of $P_{sex}$ meant that it did not contribute significantly to the overall structure. 
The graph walking algorithm was able to divide the network into three groups, but had a modularity of 0.17, which indicates that the groups are only weakly differentiated.

The widespread nature of multilocus genotypes in both wmn and production fields with relatively small values of $P_{sex}$ may indicate the spread of inoculum between regions. 
It has previously been shown that infections can be transmitted through seed [@botelho2013performance], but seedborne transmission is thought to be of insignificant epidemiological importance [@strausbaugh2003management].
Thus, we hypothesize that shared genotypes between populations may arise due to transmission events of seed or sclerotia.
However, because we observe population structure based on Region, we speculate that these transmission events are rare.

@@

@@

With the exception of the WA Region, populations that were sampled across several years appeared to be relatively stable over time with overlapping distributions in the DAPC (i.e. NE and MI, Fig. \@ref(DAPC-RY)). 
DAPC is based on the principal components of Euclidean distance between genotypes [@jombart2010discriminant]. 
Unlike Bruvo's distance, Euclidean distance does not take into account the magnitude of the difference between alleles, which could inflate the distance measure in the presence of private alleles [@bruvo2004simple]. 
We found no evidence of private alleles in the Mexico and CA isolates, suggesting that this pattern separating these populations from the others was not an artifact.
